# Setup

## Import Libraries

```{R}
library(readxl)
library(dplyr)
library(ggplot2)
```

## Transform Data

```{r}
# Convert test variable to factor
df$test <- as.factor(df$test)

# Combine imp_1, imp_2, imp_3, imp_4, imp_5 because Sites 1-5 are under the same network.
df <- df %>%
  mutate(imp_1_5 = imp_1 + imp_2 + imp_3 + imp_4 + imp_5)

# Combine all impressions
df <- df %>%
  mutate(imp_total = imp_1_5 + imp_6)
```

```{r}
# Compare sites 1-5 impressions across test & control
t.test(df$imp_1_5 ~ df$test)
```

```{r}
# Compare site 6 impressions across test & control
t.test(df$imp_6 ~ df$test)
```

## Check Summary Stats

```{r}
summary_stats <- df %>%
  group_by(test) %>%
  summarise(
    mean_imp_1_5 = mean(imp_1_5, na.rm = TRUE),
    mean_imp_6 = mean(imp_6, na.rm = TRUE),
    mean_imp_total = mean(imp_total, na.rm = TRUE),
    count_purchase = sum(purchase, na.rm = TRUE)
  )
print(summary_stats)
```

```{r}
# Power analysis for a two-sample t-test
power.t.test(d = 0.05,       # Expected effect size (difference in means)
           sig.level = 0.05, # Significance level (alpha)
           power = 0.8,      # Desired power (80%)
           type = "two.sample", 
           alternative = "two.sided") # Two-tailed test
```

The test shows each group has to be at least 6280 data point. The
experiment has over millions of testing point which leads to overpower.
It's a positive sign.

## Check Distribution

```{r}
hist(df$imp_1_5)
hist(df$imp_6)
hist(df$imp_total)
```

The distribution for impressions is heavily skewed to the right.

# Model Fitting

## 1. Is online advertising effective for Star Digital?

## Check for relationships between purchase vs. test group and impressions (separately)

Is there a relationship between purchase and if the consumer is part of
the test group

-   OR their impression count for websites 1-5 OR their impression count
    for website 6?

```{r}
model_interaction <- glm(purchase ~ test + imp_1_5 + imp_6, 
                         data = df, family = "binomial")
summary(model_interaction)
exp(coef(model_interaction))
```

**ANSWER:**

-   test1 : p-value: 0.0783 \> 0.05 –\> marginally statistically
    significant

    -   odds: Consumers in the test group have a 7.62% increase in odds
        of purchasing compared to those in the control group.

-   imp_1_5 : p-value: \<2e-16 \< 0.05 –\> statistically significant

    -   odds: Each 1 increase in imp_1_5 increases the odds of purchase
        by 3.27%.

-   imp_6 : p-value: 9.27e-07 \< 0.05 –\> statistically significant

    -   odds: Each 1 increase in imp_6 increases the odds of purchase by
        1.45%.

------------------------------------------------------------------------

## Is there a frequency effect of advertising on purchase? In particular, the question is whether increasing the frequency of advertising increases the probability of purchase?

## Check for relationships between purchase vs. test group and impressions (together)

------------------------------------------------------------------------

Is there a relationship between purchase and

-   impression count for websites 1-5

-   GIVEN the consumer is part of the test group?

```{r}
model_interaction <- glm(purchase ~ test * imp_1_5, 
                         data = df, family = "binomial")
summary(model_interaction)
exp(coef(model_interaction))
```

ANSWER:

-   test1:imp_1_5

    -   p-value: 9.11e-05 \< 0.05 –\> statistically significant

    -   odds: Each 1 increase in imp_1_5, given the consumer is part of
        the test group, increases the odds of purchase by 1.49%.

------------------------------------------------------------------------

Is there a relationship between purchase and

-   impression count for website 6

-   GIVEN the consumer is part of the test group?

```{r}
model_interaction <- glm(purchase ~ test * imp_6, 
                         data = df, family = "binomial")
summary(model_interaction)
exp(coef(model_interaction))
```

ANSWER:

-   test1:imp_6

    -   p-value: 0.00347 \< 0.05 –\> statistically significant

    -   odds: Each 1 increase in imp_6, given the consumer is part of
        the test group, increases the odds of purchase by 1.72%.

Summary : increasing the frequency of advertising increases the
probability of purchase by a small percentage showing above

------------------------------------------------------------------------

## Check for relationships between purchase vs. impressions

------------------------------------------------------------------------

Is there a relationship between purchase and the consumers' impression
count for websites 1-5?

```{r}
model_interaction <- glm(purchase ~ imp_1_5, 
                         data = df, family = "binomial")
summary(model_interaction)
exp(coef(model_interaction))
```

ANSWER:

-   imp_1_5

    -   p-value: \<2e-16 \< 0.05 –\> statistically significant

    -   odds: Each 1 increase in imp_1_5 increases the odds of purchase
        by 3.30%.

------------------------------------------------------------------------

Is there a relationship between purchase and

-   the consumers' impression count for website 6?

```{r}
model_interaction <- glm(purchase ~ imp_6,
                         data = df, family = "binomial")
summary(model_interaction)
exp(coef(model_interaction))
```

ANSWER:

-   imp_6

    -   p-value: 1.24e-11 \< 0.05 –\> statistically significant

    -   odds: Each 1 increase in imp_6 increases the odds of purchase by
        2.00%.

## Which sites should Star Digital advertise on? In particular, should it put its advertising dollars in Site 6 or in Sites 1 through 5?

# Impression Mean Comparison

------------------------------------------------------------------------

Do the means of the consumers' impression count

-   For websites 1-5

-   Differ based on PURCHASE group

-   Given they are part of the TEST group?

```{r}
t.test(imp_1_5 ~ purchase, data = df %>% filter(test == 1))
```

ANSWER:

-   p-value: \<2.2e-16 \< 0.05 –\> statistically significant

-   Difference: 9.07 - 3.07 = 6.00

-   Yes, the average impression count for websites 1-5 for consumers
    that are part of the TEST group is 9.07 for those that purchased
    compared to 3.07 for those that did not - a 6.00 difference!

------------------------------------------------------------------------

Do the means of the consumers' impression count

-   For websites 1-5

-   Differ based on PURCHASE group

-   Given they are part of the CONTROL group?

```{r}
t.test(imp_1_5 ~ purchase, data = df %>% filter(test == 0))

```

ANSWER:

-   p-value: \<1.509e-10 \< 0.05 –\> statistically significant

-   Difference: 8.68 - 3.60 = 6.08

-   Yes, the average impression count for websites 1-5 for consumers
    that are part of the CONTROL group is 8.68 for those that purchased
    compared to 3.60 for those that did not - a 6.08 difference!

------------------------------------------------------------------------

Do the means of the consumers' impression count

-   For website 6

-   Differ based on PURCHASE group

-   Given they are part of the TEST group?

```{r}
t.test(imp_6 ~ purchase, data = df %>% filter(test == 1))
```

ANSWER:

-   p-value: 3.964e-13 \< 0.05 –\> statistically significant

-   Difference: 2.08 - 1.46 = 0.62

-   Yes, the average impression count for website 6 for consumers that
    are part of the TEST group is 2.08 for those that purchased compared
    to 1.46 for those that did not - a 0.62 difference!

------------------------------------------------------------------------

Do the means of the consumers' impression count

-   For website 6

-   Differ based on PURCHASE group

-   Given they are part of the CONTROL group?

```{r}
t.test(imp_6 ~ purchase, data = df %>% filter(test == 0))
```

ANSWER:

-   p-value: 0.206 \> 0.05 –\> NOT statistically significant

-   Difference: 2.13 - 1.61 = 0.52

-   Yes, the average impression count for website 6 for consumers that
    are part of the CONTROL group is 2.13 for those that purchased
    compared to 1.61 for those that did not - a 0.52 difference!

-   However, these results are NOT statistically significant, so we
    cannot accept there is a difference in average impression count for
    website 6 for consumers that are part of the CONTROL group between
    those that purchased and those that did not.

------------------------------------------------------------------------

Do the means of the consumers' impression count

-   For websites 1-6 (total)

-   Differ based on PURCHASE group

-   Given they are part of the TEST group?

```{r}
t.test(imp_total ~ purchase, data = df %>% filter(test == 1))
```

ANSWER:

-   p-value: 2.2e-16 \< 0.05 –\> statistically significant

-   Difference: 11.15 - 4.53 = 6.62

-   Yes, the average impression count for websites 1-6 for consumers
    that are part of the TEST group is 11.15 for those that purchased
    compared to 4.53 for those that did not - a 6.62 difference!

------------------------------------------------------------------------

Do the means of the consumers' impression count

-   For websites 1-6 (total)

-   Differ based on PURCHASE group

-   Given they are part of the CONTROL group?

```{r}
t.test(imp_total ~ purchase, data = df %>% filter(test == 0))
```

ANSWER:

-   p-value: 7.924e-10 \< 0.05 –\> statistically significant

-   Difference: 10.81 - 5.21 = 5.60

-   Yes, the average impression count for websites 1-6 for consumers
    that are part of the CONTROL group is 10.81 for those that purchased
    compared to 5.21 for those that did not - a 5.60 difference!

Summary : Websites 1-5 have a much greater difference in impression
count between purchase and no purchase groups for both TEST and CONTROL
groups compared to Website 6.
